Kronos \& Krios: Evidence for accretion of a massive, rocky planetary system in a comoving pair of G dwarfs

### 2017-06-15 paper/ms.tex
Tweaks from Bedell's comments

Here, we report and discuss the discovery of a comoving pair of solar twin stars,
HD~240430 and HD~240429, with unusual chemical abundance differences
that strongly suggest accretion of planetary material by the two stars.
Throughout the \documentname, we nickname the two stars \bizarreone\
(HD~240430) and \sunanalog\ (HD~240429).
We use the following convention for chemical abundances of stars: \elemH{X} is
the ratio of number density of element \elem{X} to \elem{H} relative to the
solar value.
The absolute abundance of \elem{X} is $A(\elem{X}) = 12 + \log_{10}
(n_\elem{X}/n_\elem{H})$ where $n_\elem{X}$ is the number density of element
\elem{X}.
In \sectionname~\ref{sec:data} we present the astrometric and spectroscopic data
about the two stars relevant to the present discussion.
In \sectionname~\ref{sec:discussion} we discuss possible interpretations of
the abundance difference between the pair.
We summarize our discussions in \sectionname~\ref{sec:summary}.

@@

How much mass of rocky material is needed to explain an increment of
$\approx 0.2$~dex?
We carry out simple toy calculations of expected $\Delta\elemH{X}$
in a Sun-like star's atmosphere by adding certian mass of bulk Earth composition
under these simplifying assumptions:
\begin{itemize}
  \item The material added is instantly and completely mixed.
  \item The atmospheric composition that we measure is identical throughout
    the star's radiative and convective zone.
  \item The surface abundance of the star has been altered only by the
    accretion event(s).
\end{itemize}

We take the solar abundances, $\elemH{X}$, of element \elem{X}
(\citealt{Asplund:2009aa}) which can be converted to mass fraction as
\begin{equation}
  f_{X,\mathrm{photo}} = \frac{10^{\elemH{X}} m_X}{\Sigma_X 10^{\elemH{X}} m_X}
\end{equation}
where $m_X$ is the mass of each element in e.g., atomic mass unit.
Assuming that the added material has a total mass $M_\mathrm{add}$, and the
mass fraction in each element $f_{X,\mathrm{add}}$,
the abundance difference is
\begin{equation}
  \Delta\elemH{X} = \log_{10} \frac{f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}
    + f_{X,\mathrm{add}}\,M_\mathrm{add}}
    {f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}}
\end{equation}
where $f_\mathrm{CZ}$ is the fraction of the star's mass in the convective envelope.
We take the composition of bulk Earth from a chondritic model of the Earth
(\citealt{mcdonough2001composition}).

>>>>

Here, we report and discuss the discovery of a comoving pair of G stars,
HD~240430 and HD~240429, with unusual chemical abundance differences
that strongly suggest accretion of planetary material by the two stars.
Throughout the \documentname, we nickname the two stars \bizarreone\
(HD~240430) and \sunanalog\ (HD~240429).
We use the following convention for chemical abundances of stars: \elemH{X} is
the ratio of number density of element \elem{X} to \elem{H} relative to the
solar value.
The absolute abundance of \elem{X} is $A(\elem{X}) = 12 + \log_{10}
(n_\elem{X}/n_\elem{H})$ where $n_\elem{X}$ is the number density of element
\elem{X}.
In \sectionname~\ref{sec:data} we present the astrometric and spectroscopic data
about the two stars relevant to the present discussion.
In \sectionname~\ref{sec:discussion} we discuss possible interpretations of
the abundance difference between the pair.
We summarize our discussions in \sectionname~\ref{sec:summary}.

@@

How much mass of rocky material is needed to explain an increment of
$\approx 0.2$~dex?
We carry out simple toy calculations of expected $\Delta\elemH{X}$
in a Sun-like star's atmosphere by adding certain mass of bulk Earth composition
under these simplifying assumptions:
\begin{itemize}
  \item The material added is instantly and completely mixed.
  \item The atmospheric composition that we measure is identical throughout
    the star's radiative and convective zone.
  \item The surface abundance of the star has been altered only by the
    accretion event(s).
\end{itemize}

We take the solar abundances, $\elemH{X}$, of element \elem{X}
(\citealt{Asplund:2009aa}) which can be converted to mass fraction as
\begin{equation}
  f_{X,\mathrm{photo}} = \frac{10^{\elemH{X}} m_X}{\Sigma_X 10^{\elemH{X}} m_X}
\end{equation}
where $m_X$ is the mass of each element in e.g., atomic mass unit.
Assuming that the added material has a total mass $M_\mathrm{add}$, and the
mass fraction in each element $f_{X,\mathrm{add}}$,
the abundance difference is
\begin{equation}
  \Delta\elemH{X} = \log_{10} \frac{f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}
    + f_{X,\mathrm{add}}\,M_\mathrm{add}}
    {f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}}
\end{equation}
where $f_\mathrm{CZ}$ is the fraction of the star's mass in the convective envelope.
We take the composition of bulk Earth from a chondritic model of the Earth
(\citealt{mcdonough2001composition}).
Similar calculations have been performed by \citet{Chambers:2010aa} and
\citet{Mack:2014aa,Mack:2016aa}.
